\documentclass[9.5pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[scale=0.75,top=1cm,bottom=1cm,left=1cm,right=1cm]{geometry}

% Personal data
\name{Ama}{Bandara}
\title{Senior Security Consultant}                              
\address{Kelaniya, Sri Lanka 11600}                 
\phone[mobile]{+94776388647}                       
\email{amabandarasp@gmail.com}                      
\social[linkedin]{ama-s-bandara}                    
\quote{\centerline{\textbf{\large{PENETRATION TESTING {\textbar{}} VULNERABILITY ASSESSMENTS {\textbar{}} OFFENSIVE SECURITY}}}}

% Begin document
\begin{document}
\makecvtitle

\section{Summary}
\cvitem{}{
Accomplished Senior Security Consultant with extensive experience conducting comprehensive penetration testing, vulnerability assessments, and security audits across diverse industries. Leveraging offensive security tools proficiently, including Kali Linux, Metasploit, Burp Suite, Nmap, and Wireshark, to identify potential risks and deliver actionable recommendations enhancing clients' security posture. Proven expertise in web application testing, infrastructure assessments, mobile application security testing, wireless security assessments, and executing phishing simulations to evaluate overall security infrastructure robustness.
}

\section{Experience}
\cventry{Dec 2020 -- Present}{Tech Lead}{Takumi Tech Pvt Ltd}{Colombo, Sri Lanka}{}{
Spearheaded a team of 5, developing BillPal, an expense management system leveraging Flutter for mobile app, Angular for web app, and .NET Core for web API, optimizing application scalability, security, and user experience through Firebase Firestore integration, OCR scanning functionality, expense prediction analytics, and data visualization.
\begin{itemize}%
\item[--] Orchestrated the development of BillPal, an expense management system, utilizing Flutter for mobile app, Angular for web app, and .NET Core for web API, enhancing application scalability and security while prioritizing an intuitive user experience.
\item[--] Integrated OCR scanning of bills using ML Vision Flutter package, empowering users to effortlessly capture and categorize expense data, resulting in a 25\% surge in user engagement and retention.
\item[--] Implemented Firebase Firestore for secure bill data storage and predictive analytics to forecast future expenses weekly and monthly, enabling users to proactively manage their finances with data-driven insights.
\item[--] Visualized expense analytics on mobile and web using Fusion Sync Fusion Charts, providing users with intuitive insights into their spending patterns, facilitating data-driven financial decisions and optimizing resource allocation.
\item[--] Championed the adoption of clean architecture, SOLID principles, dependency injection, and rigorous code reviews, fostering a maintainable and extensible codebase while ensuring adherence to industry best practices, promoting long-term sustainability..
\end{itemize}
}

\cventry{Feb 2019 -- May 2020}{Senior Software Engineer}{ESSHVA TECHQ (PVT) Ltd}{Colombo, Sri Lanka}{}{
Solely responsible for architecting and implementing the backend infrastructure for WebStory, a social network platform, leveraging microservices architecture, .NET Core REST APIs, Identity Server authentication, MongoDB for friend management and content sharing, MSSQL for user data storage, and integrating AWS services for scalability and real-time notifications.
\begin{itemize}%
\item[--] Designed and orchestrated the backend architecture for WebStory, a social network platform, employing a microservices architecture with .NET Core REST APIs, Identity Server for authentication, and MongoDB for friend management, post sharing, and commenting functionalities.
\item[--] Implemented real-time notifications using SignalR, ensuring users remain engaged and informed about the latest activities on the platform, resulting in a 35\% surge in user retention and platform stickiness.
\item[--] Leveraged AWS services, including API Gateway, EKS, Docker, and load balancing, to ensure high availability, scalability, and efficient resource utilization, enabling the platform to handle peak traffic without performance degradation.
\item[--] Implemented the Saga pattern and CQRS with event sourcing, enhancing system reliability, maintainability, and enabling auditing capabilities for critical operations, promoting transparency and accountability.
\item[--] Collaborated closely with the US client, gathering requirements, and working in a production support team, ensuring timely resolution of critical bugs and performing hotfixes to maintain system stability and uptime..
\end{itemize}
}

\cventry{Feb 2017 -- Jan 2019}{Full Stack Software Engineer}{E-Wings Solutions (PVT) Ltd}{Malabe, Sri Lanka}{}{
Contributed to the development of HostWeb, a custom CMS for automobile companies, implementing inventory management, advertisement management, lead tracking, SEO modules, and Craigslist ad integration, collaborating with a team of 3 developers following Agile methodologies.
\begin{itemize}%
\item[--] Developed key modules for HostWeb, a custom CMS for automobile companies, including inventory management with drag-and-drop widgets, advertisement management, lead tracking, SEO optimization, and Craigslist ad integration functionalities.
\item[--] Implemented a robust inventory management system, empowering automobile companies to efficiently manage their stock, track inventory levels, and ensure accurate and up-to-date information for customers, optimizing customer experience and satisfaction.
\item[--] Integrated advertisement management capabilities, enabling clients to create, schedule, and track the performance of their advertising campaigns, resulting in a 20\% increase in lead generation and customer acquisition.
\item[--] Developed a comprehensive lead tracking module, providing clients with valuable insights into customer behavior, enabling data-driven marketing strategies and enhancing customer acquisition efforts, driving business growth and profitability.
\item[--] Collaborated seamlessly with a team of 3 developers, following Agile methodologies with 2-week sprints, ensuring timely delivery of new features and enhancements while maintaining high code quality standards, promoting efficiency and productivity..
\end{itemize}
}
\cventry{Jan 2013 -- Jan 2016}{Full Stack Web Developer}{Narconon Europe}{Helsingr, Denmark}{}{
}

\section{Projects}

% BillPal
\cvitem{BillPal -- Mobile Web Expense Management System (Dec 2020 -- Current)}{
\begin{itemize}
\item[--] \textbf{Role:} Lead Developer
\item[--] \textbf{Technologies Used:} .NET Core, Angular, Flutter, Firebase, GCP, Lambda functions, TDD, SOLID, DI, Identity Server, GitLab, Redmine, JIRA, Clean Architecture, BLoC pattern
\item[--] \textbf{Contributions and Achievements:}
\begin{itemize}
    \item[--] Led teams in building robust solutions, ensuring adherence to best practices in software design and coding.
    \item[--] Mentored team members to enhance code quality and consistency.
    \item[--] Implemented OCR for bill scanning, Firebase Firestore for data storage, and used Fusion Charts for analytics and report generation.
    \item[--] Introduced clean architecture and guided the team through the development of both mobile and web applications.
\end{itemize}
\item[--] \textbf{Outcome/Impact:} Elevated BillPal's functionality, resulting in a comprehensive expense management system with advanced predictive analytics and reporting capabilities.
\end{itemize}
}

% Web E Story
\cvitem{Web E Story -- Microservices-based Social Network (Feb 2019 -- May 2020)}{
\begin{itemize}
\item[--] \textbf{Role:} Backend Developer
\item[--] \textbf{Technologies Used:} C\#, .NET Core Web API, NUnit, React, Redux, AWS, EKS, RabbitMQ, Docker, Identity Server, MongoDB, MS SQL, SOLID, DI, Jenkins, JIRA
\item[--] \textbf{Contributions and Achievements:}
\begin{itemize}
    \item[--] Developed backend functionalities and maintained best practices.
    \item[--] Enhanced the social network platform with a comprehensive friend management system, notification features, and data encryption.
    \item[--] Implemented microservices architecture, ensuring scalable and efficient backend services.
\end{itemize}
\item[--] \textbf{Outcome/Impact:} Successfully launched a unique social networking platform that allows users to share experiences securely and engage within a controlled environment.
\end{itemize}
}

% Brainweber
\cvitem{Brainweber -- Big-Data Analysis (Feb 2019 -- May 2020)}{
\begin{itemize}
\item[--] \textbf{Role:} Full Stack Developer
\item[--] \textbf{Technologies Used:} C\#, .NET Core, SignalR, SyncFusion, Dapper, Azure, Power BI
\item[--] \textbf{Contributions and Achievements:}
\begin{itemize}
    \item[--] Utilized asynchronous programming for improved responsiveness and resource utilization.
    \item[--] Implemented customizable dashboards with real-time data analysis capabilities.
    \item[--] Introduced test automation to enhance efficiency and reduce post-release bugs.
\end{itemize}
\item[--] \textbf{Outcome/Impact:} Facilitated informed decision-making for users through advanced data analysis tools, contributing to the platform's success as a comprehensive big data analysis solution.
\end{itemize}
}

% Add more projects using the same structure as above

\section{Skills}
\cvitem {Programming}{ C\#, JavaScript, TypeScript, SQL}
\cvitem {Frameworks}{ .NET Core, ASP.NET, Angular, React, Redux, Entity Framework}
\cvitem {Databases}{ Microsoft SQL Server, MongoDB, Firebase Firestore}
\cvitem {Cloud Computing}{ AWS (EKS, API Gateway, Docker, EC2), Microsoft Azure}
\cvitem {Offensive Security Tools}{ Kali Linux, Metasploit, Burp Suite, Nmap, Wireshark}
\cvitem {Methodology}{ Agile (Scrum, Kanban), SOLID, DDD, TDD, CQRS, Event Sourcing}
\cvitem {Web Services}{ REST APIs, SignalR, Identity Server, JWT Authentication}
\cvitem {Testing}{ Penetration Testing, Vulnerability Assessments, Unit Testing, Integration Testing}
\cvitem {Other Technologies}{ OCR, ML Vision, Power BI, Fusion Charts, RabbitMQ, Redis, Sentry}

\cvitem{Soft skills}{Analytical and Problem-Solving Skills, Collaborative and Teamwork Oriented, Ability to Lead and Mentor Teams, Professionalism and Client Confidentiality, Strong Communication and Interpersonal Skills, Independent Work Ethic and Self-Motivation}
 

\section{Education}
\cventry{}{Bachelor of Science in Computer Science}{University of Colombo}{Colombo, Sri Lanka}{}{}

\end{document}
